---
title: "EEEEEEEEE testing"
author: Muhaha
output: github_document
---

Workflow to :

1. Prepare R environment
2. Download data
3. Tidy and gap filling data
4. Summary statistics report

## 1. Prepare R environment

Load relevant packages

```{r setup}
knitr::opts_chunk$set(echo=TRUE) #all code chunks will be shown in final file
library (dataRetrieval)
library (tidyverse)
library (zoo)
library (lubridate)
```

## 2. Download data

We will use `readNWISdv` from package `dataRetrieval` package to get data stream data for USGS.

```{r download}
usgs_id <- "07141220" #gage id for Kansas River
data_raw <- readNWISdv(siteNumbers = usgs_id, parameterCd = "00065", startDate = "2018-10-01", endDate = "2021-09-30")
summary(data_raw)

write.csv(data_raw, "data/Example_Raw.csv")
```

## 3. Tidy and gap filling data

```{r clean_data}
data_tidy <- data_raw %>% 
  rename (stage_ft = X_00065_00003, stage_QAcode = X_00065_00003_cd) %>%
  select(-agency_cd, -site_no)

head (data_tidy)

ggplot(data_tidy) + geom_line(aes(x=Date, y=stage_ft)) 

#check for missing dates
first_date <- min(data_tidy$Date)
last_date <- max(data_tidy$Date)
dates <- seq(first_date,last_date, by= "day")
length(dates) == length(data_tidy$Date)

#fill the gaps
missing_dates <- dates[!(dates %in% data_tidy$Date)]
new_data <- data.frame(Date=missing_dates, stage_ft=NA, stage_QAcode="Gapfill" )

data_clean <- bind_rows(data_tidy, new_data) %>% arrange (Date)
summary(data_clean)

#fill the gaps with appoximation
data_clean$stage_ft <- na.approx(data_clean$stage_ft)

ggplot(data_clean, aes(x=Date, y=stage_ft, color= stage_QAcode)) + geom_point()

write.csv(data_clean, "data/Example_Cleaned.csv")
```

## 4. Summary statistics report

we analyzed data from USGS gage `r usgs_id`. During the period of record, the maximum stage was `r max (data_clean$stage_ft)` and the minimum stage was `r min (data_clean$stage_ft)`.
There was total of `r length(missing_dates)` missing dates that we filled using linear interpolation.